\pagestyle{fancy}
\lhead{OCR A-Level Computer Science}
\chead{\thepage}
\rhead{Jonathan Kasongo}
\lfoot{Candidate number: N/A}
\rfoot{Centre number: N/A}

\chapter{Analysis}

\section{Context}
\label{sec:context}

My client Axel Alabi has asked me to create an interactive
video conferencing application to allow others to view talks 
in realtime. The current solution is to use the Zoom 
video conferencing application. While it is true that the 
application is technically sound and can work fine, there is a
large number of elderly users that also try to connect to the 
conferences. These users often don't fully understand how to 
correctly use the application and then end up accidentally 
disturbing the conference/talk \footnote{From this point 
forward we will avoid using "conference/talk", and simply
replace it with "conference".}, by leaving their microphone's
on, accidentally raising their hands and so on. This makes my
client's job difficult since he is in charge of managing the 
Zoom call. To combat this situation he would like a 
simple and user friendly video conferencing application that
provides the features needed for people to view and interact
with the conferences in real time. This includes 
features like (but not limited to) audience participation,
the ability to speak to others via one's microphone and the
ability to vote on polls. The application should be
created specifically to help elderly people have a better 
experience whilst watching any conferences, so may also
include extra accessibility features to ensure comfortable
viewing for all, irrespective of one's age and/or disabilities.

\section{Justifying a computational method}
\label{sec:computational}

The population of elderly ones in the UK has seen a 52\% 
increase in the last 40 years. This group of people includes
a large number of those who are isolated and feel a sense of 
loneliness in their lives. However through video conferencing
these ones gain the ability to socialise and interact with 
others from the comfort of their homes. This is especially 
useful as many elderly ones have limited mobility or are bed 
bound. Without regular opputunities to socialise and interact 
humans become depressed and our mental health will begin to 
decline. By developing software to enable those disabled 
people to talk to others can improve the quality of their 
mental health significantly. When people are limited by their 
disabilities or by their illnesses the oppurtunities to go and
talk to new people in real life become far and few between. For
these people real physical interactions may not be possible,
meaning that a computational solution to their problem is not
just preferred but necessary. \vspace{0.2cm}

Accessible video conferencing software is useful to young 
people aswell. People like my client also have problems with 
current systems. In order for him to carry out his job 
effectively he requires a simple and reliable computational
solution. Current systems pose a challenge for elderly people 
to use, which in turn means that my client has to spend a good
majority of his time helping people set up their webcams,
microphones or other settings. If my client instead had access
to video conferencing software that was easy for elderly people
to understand how to use comfortably his job would be 
simplified significantly, and in order to create that new 
software it is evident that a computational method can be 
used. To justify this claim we examine the average download
speeds for UK resedentials and compare it to the amount of 
download bandwidth needed to transfer clear video and audio 
for 1 second. \textit{"Average download speed of UK home 
broadband connections was 69.4 Mbit/s"} as of 2023 \cite{data}.
To compare this speed we use data from a study that took place
at the University of Chicago \textit{"On average, these
applications used about 1-2 Mbits/s of download bandwidth"}
\cite{chicago}. Even when taking the worst case of 2 Mbits/s
of download bandwidth, only $\approx 2.88\%$ of the broadband
is used. Moreover we have evidence from the previous systems 
like Zoom that were in use, that creating such an application
is definitely amenable to a computational approach.
Applications such as Zoom are able to transfer 1080p quality
video and audio data at 30 FPS with millions of users 
worldwide. These results demonstrate the validity and
feasability of a computational approach to solving this
problem. \vspace{0.2cm}

Decomposition is a computational method that involves breaking
down complex problems into multiple smaller and more 
manageable problems. Real-time video/audio feeds is the ability
for a system to take the live video and audio from a user's 
device share it to others with negligable latency. We justify
the feature of having real-time audio and video by examining 
the client's request as in \ref{sec:context}. \textit{"My 
client ... asked me to create an interactive video conferencing
platform."} Oxford Languages define a videoconference to be 
\textit{"a conference in which participants in different 
locations are able to communicate with each other in sound and
vision."} Hence in order to satisfy the client's request we 
will need to have real-time video/audio feeds. A justification
of whether or not real-time video/audio is computationally 
feasible was given in the previous paragraph.
The problem of sharing real-time audio/video feeds between
users can be decomposed into numerous sub-problems that are
easier to accomplish. For example we could break this problem
into 4 sub-problems:

\begin{enumerate}
  \item Establish a connection to the other user's computers 
  \item Ensure user has connected a suitable webcam/microphone
  \item Access the webcam/microphone using the relevant API's
  \item{Send the video/audio data to the other users in the 
        conference}
\end{enumerate}

Breaking larger problems into multiple simpler problems 
reduces the complexity of a system and promotes a  
maintainable system. Rather than trying to debug a large and
complex system, it is much easier to debug a single function 
or class
that accomplishes only 1 task. This is because the large and 
complex system may be throwing errors for a multitude of 
reasons, perhaps it could also be throwing errors because of
one mistake that was written in the code some several hundred
lines ago. With smaller and more concise code organised into
functions and similar structures, we can tell exactly where the
code is throwing an error and start working on resolving the 
issue immediately. This problem is amenable to a computational 
approach as we are able to improve the maintainability of our
codebase by applying the technique of decomposition. Moreover
decomposition allows for a much simpler approach to problem 
solving in programming. When we face a large and complicated 
task we can first decompose the problem as we did in the 
example above, and then piece together those smaller solutions
to the sub-problems, into 1 solution that achieves our intended
goal. \vspace{0.2cm}

Often once we have decomposed a problem, patterns emerge from 
the smaller decomposed problems. In recognising these patterns
we can reduce the amount of code needed to solve each 
sub-problem by placing the common operations of each 
function/class into a function/class of it's own. In order to 
ensure these repetitive actions aren't found in my code I will
employ the use of the DRY software development principle. 
That is the "\textbf{D}on't \textbf{r}epeat \textbf{y}ourself"
principle. The purpose of the DRY principle is to avoid 
writing redundant code by replacing it with abstractions. This
principle guarentees clear and concise code. One feature of 
the problem that could benefit from pattern recognition is the 
username and passcode system. A detailed justificaiton for this
feature is provided in section \ref{sec:features} under the
sub-heading \textit{Usernames and passwords to join a call}.
There are 2 cases in which we would need to check usernames
and passwords, those are when the user initially logs into 
their account and when the user enters a passcode to enter a
video conference. Instead of writing 2 seperate pieces of
code to check for the correct username and password I could
apply pattern recognition and instead implement 1 function 
called \code{Check\_User\_and\_passcode()} to be used in both 
cases. We have seen that this problem is definitely amenable 
to a computational approach, through the application of
pattern recognition to ensure clarity and conciseness in our 
codebases. \vspace{0.2cm}

As mentioned in the above paragraph abstraction is another 
computational technique that is suited to being used in my 
solution. Abstraction is the process of removing unnecessary
details, and only keeping in the parts of the solution that are
important. Abstraction could be applied to the design of the 
UI of my application. The main focus of this application should
be for it to be simple and easy to grasp as highlighted by my 
client in section \ref{sec:research}. So in the design of my
UI I will not give the user every single piece of information
available about the call because the vast majority of that 
information will be useless to them. Furthermore it can be 
argued that the presentation of less pieces of information is
better for the user's mental health than the presentation of
large amounts of information \cite{overchoice}. When humans 
have too many options we become unable to make descisions, so
by limiting the amount of information available to the user we
allow them to focus on the few important configurations that
they should be 
in control of, in turn permitting them to give the majority of
their attention to whomever they are having a call with. This 
appropiately demonstrates the amenability of applying
abstraction in our final application. This choice will enhance
the user's experience while on our webpage and make the design
less cluttered and more aesthetically pleasing, making the 
application more desirable to use.  \\ \vspace{0.2cm}

The final computational technique is algorithmic thinking. 
Algorithmic thinking is the process of creating a finite 
sequence of steps in order to solve a given problem. Another 
one of the main objectives for the application is for it to be
accessible to all. Adding the option to have macros, 
(programmable keys that are set to perform common actions) 
can prove to be very convienient for those with limited
mobility. If the person cannot use a mouse comfortably, then 
they will have the ability to program a selected key/button to 
be able to perform pre-determined tasks like turning video
on/off and muting/unmuting the microphone. Algorithmic thinking
can be applied when implementing this feature. The task can 
be broken into a number of finite steps like so: \\

\begin{enumerate}
  \item Ask the user what button they would like to use for the macro.
  \item Update the relevant class to ensure that the action can now occur via the macro.
  \item Save this configuration onto their account through the database.
\end{enumerate}

The approach to use algorithmic thinking is justified innately
by the nature of problem-solving. Algorithmic thinking is not
just convienient when applied in the example of implementing
macros, rather it is essential to the implementation of nearly
every feature that the finished system will include. If we did
not need to apply the technique of algorithmic thinking when
programming, in other words we did not require any finite
sequence of steps to solve the problem, it means one of two
things. Either the problem needed no sequence of steps because
it was solved instantly or that the problem can be solved
using an infinite sequence of steps. In the first case if the
problem needed no steps to solve it, it must have been a
trivial problem. This case wouldn't apply to this application
because if it were trivial then my client Axel Alabi would 
easily program the system himself, because of his expertise in 
computer science. The second case implies that the problem will
be solved in an infinite amount of time, however our clients
do not have an infinite amount of time to wait for the 
solution to their problems, ruling out the second case 
entirely.

\section{Stakeholders}

\begin{tblr}{ll}
  \textbf{Stakeholder: } & Axel Alabi\\
  \textbf{Category: } & Client\\
\end{tblr}
\vspace{0.2cm}

\textit{Description.} %\\ \vspace{0.05cm}
Axel Alabi is a $22$ year old male, and is currently in charge 
of managing the video broadcasts for conferences. He also
works as a data analyst for a company specialising in analysing
geographical data, and has experience working in computer 
science and related fields. \vspace{0.2cm}

\textit{How will they use the solution?} % \vspace{0.05cm}
He would use the proposed solution in order to host
videoconferences. The new system would help the 
videoconferences run smoother as he wouldn't need to worry 
about spending his time in helping users solve their technical
issues, rather he will be able to focus solely on the
conference and whether or not the visuals and the audio are
clear. \vspace{0.2cm}

\textit{Why is it appropiate to their needs?} % \vspace{0.05cm}
The proposed solution would be appropiate for my client as it
would provide a smoother and simpler system in order to host 
videoconferences on. Furthermore the new system would ensure
that he no longer faces the challenges that were discussed
in \ref{sec:context}, like users leaving their microphone's.
This will no longer happen as the new system will have a 
clear and intentional design and the user won't obliviously 
have their microphone on, without being notified. This would 
improve his life greatly as he would be able to now focus 
solely on ensuring that video and audio is clear during the 
broadcast. In removing some of Axel's issues that he faces in
his job, he should become more content and calmer with his
work life, further demonstrating how this solution will be 
appropiate to his needs.

\vspace{0.2cm}

\noindent
\begin{tblr}{ll}
  \textbf{Stakeholder: } & {People aged $\sim$ 
  \hspace{-0.2cm} $50$ and over, with limited experience
  working with technology}\\
  \textbf{Category: } & Target users/audience\\
\end{tblr}
\vspace{0.2cm}

\textit{Description.}  
This group of users typically have limited experience working 
with technology, because they will have spent the majority of
their life without modern technologies. This will be my 
application's target audience, so it is important that the 
final solution is appropiate to their needs. \vspace{0.2cm}

\textit{How will they use it?}
These users will make use of the proposed solution by joining
videoconferences that they were invited to and interacting with
them in a manner that is convienient for them. They will be 
able to interact with the videoconference by raising their 
virtual hand, indicating to the speaker that they wish to talk.
The speaker can then give them permission to talk and properly
converse with their virtual audience. Moreover the solution
will also enrich their experience by providing options for
things like macros, enabling them to perform common tasks,
like muting/unmuting a microphone with a set button.
\vspace{0.2cm}

\textit{Why is it appropiate to their needs?}
The solution will benefit them greatly as they will now no 
longer have to ask for help from others to resolve issues with
their video conferencing application. Rather they will be able
to experience a simple, easy to work with and intuitive system
for their video conferencing. Moreover the users will now gain
the oppurtunity to improve their social lifes as they will be
able to chat withtheir loved ones and friends over their web 
browsers easily. Not only will the final solution make their 
lives more convinient but it will also provide the user with
the oppurtunity to improve their mental health through
socialising and engaging in conversation with others.
\cite{social}
\vspace{0.2cm}

\noindent
\begin{tblr}{ll}
  \textbf{Stakeholder: } & IT Staff\\
  \textbf{Category: } & Support/Maintainers\\
\end{tblr}
\vspace{0.2cm}

\textit{Description.}
The IT Staff would be experienced in working with technology
because of their qualifications in this field. These people 
would be expected to have a degree/diploma in computer science,
mathematics or another closely related field. They should also 
be expected to have significant experience in working in 
various programming languages. \vspace{0.2cm}

\textit{How will they use the solution?}
This group of users would be expected to be able to update and
maintain the system as required. The staff will use the
documentation provided along with the application in order to
understand what each function and class does along with it's
purpose. Furthermore the clear and readable code will enable
them to perform any necessary changes with ease, something
they could not have done previously with the off the shelf
software they had before. \vspace{0.2cm}

\textit{Why is it appropiate to their needs?}
The solution will be appropiate to their needs as they will be
able to access the source code of the final application and 
change the application to be tailored to work well for their 
specific needs. Additionally users who enquire about the 
security of their data when using the application will be able
to check how the application handles their data themselves.
This means that the IT staff will not have to be unsure about
answering user's queries, but rather they will be able to read
the source code and give an accurate response to the user every
time.

\subsection{Current system DFD diagram level 0 - Zoom}

\vspace{0.1cm}

\begin{figure}[h]
\label{fig:dfd}
\centering
\begin{tikzpicture}

  \node[draw, rectangle, minimum width=4cm, minimum height=1cm,
	fill=lightestgray]
	(zoom) {\large Zoom};

  \node[draw, ellipse, left=3.5cm, below=2cm,
  minimum width=3cm, minimum height=1.5cm] (user) at (zoom)
    {\large User}; 

  \node[draw, ellipse, right=3.5cm, below=2cm,
  minimum width=3cm, minimum height=1.5cm] (admin) at (zoom)
    {\large Admin};

\draw[black, -{Latex[length=2.5mm]}]
	(zoom) edge["1"]  (user);

\draw[black, -{Latex[length=2.5mm]}]
	(admin) edge["3"] [bend left=0.5cm] (user);

\draw[black, -{Latex[length=2.5mm]}]
	(user) edge["2"] [bend left=0.5cm] (admin);

\draw[black, -{Latex[length=2.5mm]}]
	(admin) edge["4"]  (zoom);

\end{tikzpicture}

\caption{Zoom DFD diagram.}
\end{figure}

\textit{An explanation of the DFD is found below. The number 
closest to each edge refers to the number in the left column of
the explanation table below.}

\begin{longtblr}[
  caption={Explanation of DFD.}
]{
  colspec={lX}, hlines, row{1}={lightestgray}
}

Edge & Commentary \\

1 & {Zoom allows user to join a video conference and gives
     user live video and audio of all the other participants 
     in the meeting. User has access to a number of 
     configurations and settings after clicking on their
     profile and then on settings.} \\

2 & {If user encounters an issue they can contact the 
     admin/host of the meeting for help. User can provide the
     context or other relevant information about the issue via
     the chat box.} \\

3 & {Admin is able to read about the user's issue via the chat
     box and they can then provide a solution to the user 
     through the the chat box. Admin is also able to invite
     other users to join the video conference by sending them
     a link or a code to join.}\\

4 & {Admin can start or stop the videoconference when
     appropiate. Admin can also interact with the app in order
     to manage the video conference. They can do things like
     spotlight speakers, screenshare images/video and mute or
     kick participants.}
  
\end{longtblr}


\section{Research}
\label{sec:research}

% Researched the problem in depth looking at existing solutions
% to similar problems, identifying and justifying suitable 
% approaches based on this research.

We begin our research by observing solutions to similar 
problems. Then justifications of suitable approaches are given
based on the existing solutions.

\subsection{Zoom}

\subsection*{Accessibility features}

Zoom is a popular closed-source video chat application,
developed by Zoom video communications. From their website 
\cite{zoom} they implement 5 major features to ensure that 
\textit{"Zoom is for everyone"}. 

\begin{itemize}
  \item Live transcriptions
  \item Automatic closed captioning
  \item Customisation of font sizes
  \item Keyboard shortcuts
  \item Screen reader support
\end{itemize}

Some advantages of this software include the fact that there
is a good amount of accessibility features able to help a wide
variety of people. For instance for those who have limited 
mobility keyboard shortcuts can be set up to conveniently 
perform common tasks, whilst those who have trouble hearing
well can enable closed captioning during the meeting.

\vspace{0.2cm}

However there are still a number of limitations with the way 
these features are implemented. Automatically generated 
closed captioning is unfortunately only available in english,
and may have varying levels of accuracy depending on external
factors such as background noise, speaker's clarity and 
profiency in spoken english.

\vspace{0.2cm}

Zoom proposes a solution to the problem of exculsivity when in 
the context of video conferencing applications. Instead of only
designing the application to be usable for one group of people
they aim to instead tailor it to cater towards 
\textit{everyone}. I believe that the wide range of
accessibility features is a big advantage of the system, and 
this could motivate the descision to implement a similar set
of features in my application. However while a good number of 
features is appreciable, it is also necessary to ensure that 
these features are simple to find and to use for an optimal 
user experience. This is justified by the fact that my client
is specifically requesting an application for those who aren't
comfortable with modern technology. To solve this problem I 
could perhaps implement a built-in tutorial that demonstrates 
how to use the accessibility features to teach the user how 
they can use the application to it's fullest potential.

\subsection{Skype}

\subsection*{Accessibility features}

Skype is a proprietary messaging and video chat application
developed by Skype technologies a subsidiary of Microsoft 
\cite{skype}. From Microsoft's support webpage Skype for 
Windows 8 and above has the 3 following key accessibility 
features.

\begin{itemize}
  \item Narrator screen reader
  \item High contrast colour settings
  \item Magnifier
\end{itemize}

These features have the advantage of being especially 
accessible for blind people or for those with low vision. The 
combination of high contrast colours along with a magnifier 
and/or screen reader ensures that low vision users can still 
make use of Skype, independently. Skype also doubles up to be
an instant messaging platform, permitting users to have all 
their conversations and other communications in 1 place.

\vspace{0.2cm}

Whilst the features mentioned are very beneficial for those 
with low vision, there is no true support for people who are
hard of hearing or have low mobility. This set of features is 
one-dimensional only catering to 1 group of less abled people.

\vspace{0.2cm}

Skype proposes a solution to \textit{"help people with 
disabilities navigate and control their device as well as get
better access to online content."} 
\footnote{Quote from \url{https://support.microsoft.com/en-gb/skype/what-accessibility-features-are-available-for-skype-89c34c52-f463-437a-b3be-2ea114c5de13}}
The solution from Skype allows for disabled ones especially 
those with reduced vision to benefit from Skype the most, as 
previously discussed. Whilst Skype offers a good set of
features for the disabled, the features that they mention on 
their website are all already either implemented on most 
popular operating systems, or can be installed as browser 
extensions with a few clicks. Therefore I believe that there is
insufficient justification to take the time to implement any 
of the features that Skype implements, and will not be 
implementing any of those features.

\vspace{0.2cm}

To obtain a better understanding of the nature of the problem
and what features should be implemented in the final solution,
I decided to collect some qualititative data through an 
interview with my client. This data should allow me to have an
insight into what the final solution should look like based
on my client's requirements and desires respectively.

\subsection{Interview}

\begin{tcolorbox}[
  boxrule=0pt, frame empty, colback=lightestgray, arc=0pt,
  breakable, colframe=white
]
  \begin{tblr}{ll}
    \textbf{Interview with Axel Alabi} & {}\\
    \textbf{Date: } \texttt{29/06/24} &
    {\hspace{-1.5cm} \textbf{Time: } \texttt{3.50pm}}
  \end{tblr}

  \vspace{0.2cm}

  \textbf{Q:} What are some of the limitations of the current
  system used for video conferencing? \vspace{0.05cm}

  \textbf{A:} It tends to be difficult for people who aren't 
  experienced with technology to properly interact in the 
  conferences. Often times participants will accidently turn 
  their microphone on or are unable to turn their microphone
  on when the speaker invites them to. \vspace{0.25cm}

  \textbf{Q:} What are some essential features that should be
  required in the final application? \vspace{0.05cm}

  \textbf{A:} Well to start the app should allow users to see 
  and hear one another in real-time, there should be a focus on
  simplicity and users should be able to raise their virtual 
  "hand" to interact with the talk. \vspace{0.25cm}

  \textbf{Q:} What are some non-essential features that would
  be desirable in the final application? \vspace{0.05cm}

  \textbf{A:} The app could perhaps provide a suite of 
  accessibility features to allow disabled ones to have a 
  comfortable viewing experience. This may include closed
  captioning, volume control and a screen reader.
  \vspace{0.25cm}

  \textbf{Q:} What operating system should the application be 
  designed for? \vspace{0.05cm}

  \textbf{A:} There is no preference for operating systems.
  \vspace{0.25cm}

  \textbf{Q:} What are the software requirements? 
  \vspace{0.05cm}

  \textbf{A:} It should be a web-based application. Any 
  suitable mainstream programming language is fine as long as 
  the code is clear enough for me and the other IT staff to 
  understand.
  \vspace{0.25cm}

  \textbf{Q:} What is your budget for the system?
  \vspace{0.05cm}

  \textbf{A:} I'd prefer the application to be completely free
  if at all possible. \vspace{0.25cm}

  \textbf{Q:} What are the security requirements?
  \vspace{0.05cm}

  \textbf{A:} There should be some form of end to end 
  encryption to ensure that hackers or others cannot access the
  video feeds. There should also be some kind of username and 
  password system in order to enter a call. Passwords should 
  also be of a good strength e.g. at least 1 symbol, capital
  and lowercase letters.
  \vspace{0.25cm}

  \textbf{Q:} How will the new system benefit you? 
  \vspace{0.05cm}

  \textbf{A:} This new system will ensure that all video 
  conferences I am in charge of managing will run much 
  smoother, not only giving me more time to work on other 
  essential tasks but also providing a better viewing
  experience for all.

\end{tcolorbox}

From this interview, I can see that my client has some features
that should definitely be included in the solution: real-time 
audio and video as well as the ability to raise and lower one's
virtual hand. Furthermore I believe that security should also 
be very important when designing the final solution. This 
should be a requirement because we don't want any of our users
to have their important data stolen during their video
conference. \vspace{0.2cm}

Bearing this in mind we should also think about suitable 
approaches to implementing a system with these features. In 
order to implement the real-time video/audio I could make use
of the WebRTC API from Google, which would enable me to 
establish secure peer to peer connections from the browser. 
Not only does this approach allow us to establish audio and 
video, but it also ensures that these connections are secure 
through the use of signalling servers. Signalling servers are
servers that manage connections between peers. To understand 
signalling servers we will go through an example. Consider 2 
users, Alice and Bob that want to have a video call. Alice 
creates an offer for Bob to connect. Consequently WebRTC 
creates a session description protocol (SDP) object. The SDP 
object holds information like media types, name of the
session and the video codec being used. This data is then 
saved to a \textit{signalling} server. Bob then reads this SDP
offer from the server and WebRTC creates a SDP answer and
writes this to the server. Alice and Bob have now established 
a peer to peer connection. In essence, signalling allows for 
users to exchange the metadata of their connection through the
WebRTC API. To justify usage of the WebRTC API, I believe it 
is first necessary to explain why I rejected the idea of
implementing an API from scratch. Unfortunately
implementations of fully functioning and secure peer to peer
API's aren't trivial at all. The time it would take to fully
understand how to implement peer to peer connections using 
VP9 packetizers \cite{vp9} and SHA-256 cryptography for data
security would simply be too time-consuming and cannot be
justified when fully functioning, tested and performant 
implementations already exist. The next 
portion of the justification covers why did I choose the
WebRTC API over other API's? WebRTC is from Google and it is 
well known that Google is a credible technology company. 
Therefore it is sensible to assume that their API is of 
highest quality publicly available right now. However, there
are alternatives to WebRTC like: VideoSDK, Twilio and 
MirrorFly. Whilst it can be acknowledged that these API's could
potentially be a better fit for my project in terms of
performance, features and simplicity, all of these alternatives
are paid for. I don't think it would be sensible to pay for
commercial API's when there are free one's like WebRTC
available that will work just fine. This reasoning is also in 
harmony with my client's request to have the application
\textit{"be completely free if at all possible."} as seen in 
the interview. 

\vspace{0.2cm}

When discussing security it is also important to discuss the 
username and password management system that may be implemented
since it is one of my client's requests. In order to design a 
system that has secure password management it will be 
beneficial to study how other industry applications have chosen
to solve the problem of managing user passwords. I chose to 
study Bitwarden, a freemium open source password management 
service. The following information was found on their 
architecture webpage \cite{Bitwarden}. As per their website 
they use the \textit{"Command and Query Responsibility 
Segregation (CQRS) pattern"}. The CQRS model developed by 
Microsoft separates reads and writes into different models. 
\textit{Commands} are used to write to the database, whilst 
\textit{queries} are used to read from the database. Each 
command and query has one \emph{single} responsibility and 
should be based on actions rather than operations on data. For
instance Microsoft give the example rather than use the
data-based command: \code{SET ReservationStatus to Reserved}
we should prefer to use the action-based command: \\
\code{Book\_Hotel\_Room()} instead. Some of the benefits of 
this model include: 

\begin{itemize}
  \item Security. It's easier to ensure that only people of authority are performing reads and writes to the database if 
they're separated.

  \item Separation of concerns. Splitting the read and write components makes the system more modular and more maintainable. 

  \item Simplified commands. Instead of directly manipulating data commands should be based on the task they try to 
achieve.
\end{itemize}

Bitwarden's servers use the MSSQL database and makes automated
nightly backups to ensure data is protected. Nightly backups 
are backups that occur every 24 hours. Moreover the 
company uses \textit{zero-knowledge encryption} so that the 
company cannot see it's users data. To ensure zero-knowledge 
encryption the compnay uses \textit{"AES-CBC 256 bit 
encryption for the data encryption and PBKDF2 SHA-256 to 
derive one's encryption key."} \footnote{Source: 
\url{https://bitwarden.com/help/what-encryption-is-used/}} 
Through this kind of encryption the company is able to have
it's users complete trust as they are sure that their data is 
safe and cannot be read by anyone other than them. Fortunately
for our case we will not have to consider implementing these
algotrithms because WebRTC provides built-in encryption.
\vspace{0.2cm}

Another concern pertaining to passwords is our method for 
checking a potential password's strength. I propose the usage
of the \texttt{zxcvbn} algorithm \cite{pass} developed by
Dropbox. This algorithm has been implemented into a number of
programming languages by the author Daniel Wheeler, so we will
simply import one of his implementations into our codebase 
ensuring that only accurate and tested code is being used. To
justify usage of the algorithm we should first 
\textit{briefly} examine exactly what the algorithm is doing.
\footnote{Note that Daniel Wheeler explains his algorithm at
a much more in-depth level in his paper, which may be found
in the citation above, if you wish to learn more.}
\texttt{zxcvbn} consists of 3 main phases: 1) matching,
2) estimation and 3) search. Throughout the rest of this
paragraph define $p$ to be some arbitrary password of length
$n$ characters. The matching phase takes contiguous
substrings of the input password and classifies
each substring as a specific pattern like a \textit{token},
\textit{date} or a \textit{repeat}. Wheeler provides the
following example in his paper; the password
\texttt{lenovo1111} will be pattern matched like so.

\[
  \underbrace{ \mathtt{lenovo} }_\text{token} \; \;
  \underbrace{ \mathtt{1111} }_\text{repeat}
\]

Different methods are used to find each class of pattern, for 
instance in order to match tokens the algorithm first takes
a password $p$ it entirely lowercase, it then checks all 
$n \cdot (n+1)/2$ non-empty substrings with a frequency ranked
dictionary, if there are symbols in $p$ it creates extra 
strings making leet substitutions \footnote{Leet substutions are symbols that are used to replace characters like the word
\texttt{@pp1e} $\rightarrow$ \texttt{apple}.}
and does the same check on these. The next phase is
estimation where we estimate the number of guesses in order
to successfully guess each match in some password. Again
for the sake of brevity we will only consider the method to 
estimate guesses for one class of pattern: \textit{bruteforce}
patterns. \textit{Bruteforce} patterns are "patterns" with no
obvious pattern and are a random string of characters like
\texttt{ae\#U*\$gmi}. The algorithm assumes that each
character will take $C := 10$ attempts to guess correctly and 
subsequently estimates $C^n$ guesses to be required to guess
the entire substring. Finally the last phase, the search looks
for an optimal sequence $s$ of length $\left|s\right|$, from
a set $S$ of all the matches found in $p$ such that: the 
sequence contiguously covers the entirety of $p$ and this 
sequence $s$ has a minimal number of guesses $m_G$ over all
matches $m$. More formally the algorithm computes

\[
  \argmin_{s \subseteq S} \left( D^{\left|s\right| -1} + 
  \left|s\right|! \prod_{m \in s} m_G \right)
\]

where $D$ is a constant that acts to bias against long
sequences that unintentionally minimise the 
$\prod_{m \in s} m_G$ term.

\vspace{0.2cm}

\textit{What are suitable approaches based on this research?}
The features that Zoom provides like keyboard shortcuts and 
custom font sizes would be suitable because they would aid the
user and allow them to have a more comfortable tailored viewing
experience. The interview also provided some valuable 
information for essential features in the system, like the 
focus on simplicity. This information guides the approach to 
the design of the system, the design should be created to 
prioritse ease of use and simplicity. Moreover we have seen 
that using the WebRTC API for peer to peer video connections
is a suitable approach because of it's security, credibility
and it's alignment with the client's goal to have the system
be free if possible. Additionally the previous paragraph 
outlined an approach to reading/writing to databases, the 
CQRS model. Usage of this model will help streamline the 
database for this system, because each command/query will be
clearly named and let the developer know exactly what 
processes are taking place at that moment. 

\section{Essential features \& their justifications}
\label{sec:features}

\textbf{Real-time audio/video feeds} \\ \vspace{0.1cm}

This will enable multiple users to connect to each other via
their browsers and view each other's webcams, as well as hear
each other in real-time. The justification for this feature is
that it is explicitly requested for by my client in our
interview, furthermore we don't have a \textit{video}
conferencing application if we cannot actually see other 
people's video feeds on our application.

\vspace{0.2cm}

\textbf{Raising one's virtual hand} \\ \vspace{0.1cm}

This feature will allow people to be able to interact with the
person giving the talk as if they were present in real life.
The virtual hand will be made visible to all participants in 
the conference so that the speaker/host will be able to ask 
the audience members to speak when appropiate. This feature
is sufficiently justified because of my client's specific 
request to implement it as a feature in the interview. 
Furthermore the implementation of this feature will help the 
migration from Zoom to our new platform be familiar as this 
feature is also found on Zoom.

\vspace{0.2cm}

\textbf{Designation of a host} \\ \vspace{0.1cm}

This feature will allow the creator of the conference to 
assign 1 or multiple people to be the \textit{host} of the 
conference. That means that these people will be in charge of 
managing the conference and will control who to admit into the
conference call, who to unmute and who to remove from the call,
and will be able to lower other's virtual hand. The
justification of this feature is that I believe there should 
always be someone of some sort of authority to coordinate and 
manage these conferences. This is very common in real life also
because without management and coordination people would be 
clueless, and anarchy would run rampant. This phenomenon has
been seen in other video chat applications more specifically,
on Zoom (e.g. Zoombombing), and in order to provide the best
experience for our users it is vital that events like this 
aren't allowed to occur.

\vspace{0.2cm}

\textbf{Usernames and passwords to join a call} \\ 
\vspace{0.1cm}

Each user will be able to choose their unique username so 
that users can easily identify one another upon joining a call.
Furthermore each user can set their own password so that their
account is protected and others cannot pretend to be them. 
Assigned to each user account will be their saved settings and
options, so that if a user has a specific configuration of 
settings that are adapted for their needs they don't have to 
set these up each time they log onto a conference. Passwords 
will be made to fit some set of requirements to ensure that 
the password is of sufficient strength. When a user creates a 
call they will be given a unique passcode that they will be 
able to share with anyone else whom they would like to invite
to the video conference. The justification of this feature is
clearly sufficient because it was explicitly requested during
my interview with the client. Moreover without a passcode 
system to enter a call anyone would be able to enter anyone
else's call, giving users no privacy at all. It would also 
cause issues very similar to the anarchy that was discussed in 
the previous paragraph.

\vspace{0.2cm}

\textbf{Simple and user friendly UI} \\ \vspace{0.1cm}

The UI should be designed in such a way that anyone could be 
able to understand how to use the application. This feature
aligns with the idea to have the system be accessible, through 
ensuring that all users are able to navigate the interface 
without asking others for help. Furthermore a nice and 
user-friendly interface makes the app more pleasant to use and
the user will only have essential information on their screens
to make sure that the interface is not cluttered or 
overcrowded. This feature is fully justified since my client 
requested this as an "essential" feature during our interview
in section \ref{sec:research}.

\section{Limitations}

\textbf{Limitation 1: } \\ \vspace{0.1cm} 

The application will require an internet connection. Since the
application makes use of the WebRTC API, we require internet 
access in order to establish any peer to peer connections.
Though accessibility is one of the main focuses of the system,
this limitation actively makes the app less accessible. This
is because people may not always have access to the internet 
whether it be due to economic, geographical or other reasons.
Hence in using the WebRTC API we have limited the number of 
potential users for our application as not everyone has 
constant access to the internet. More precisely, only 66\% of 
people have internet access in the world according to Statista.
\footnote{Source: \url{https://www.statista.com/statistics/325706/global-internet-user-penetration/}}
This limitation is sufficiently justified through the fact that
we aim to have the app be as accessible as possible, but in 
order for the application to function an internet connection is
required, alienating 34\% of the world's population as they
will be completely unable to use the system. \\ \vspace{0.2cm}

\textbf{Limitation 2: } \\ \vspace{0.1cm}

As specified in the essential features, each user will have to 
create an account with a set username and password in order to 
use the application. This means users will have to remember 
their passwords which could be difficult for this application's
target demographic. This means that the app will be
potentially inaccessible for people suffering from conditions
like amnesia or dementia, further restricting our possible 
userbase. If a user has forgotten their password they
may be forced to create a new account, which is a pain for the 
user as they would have to use a new username and notify all of
their contacts that their username has changed. It would also 
be a pain for the database as each time someone forgets their 
password a redundant account is left in the database, 
increasing the size of the database exponentially, if a user 
forgets their password multiple times. This limitation is 
justified by the fact that if this limitation is left to be
there will be consequences to both the user and also to the 
database. \\ \vspace{0.2cm}

\textbf{Limitation 3: } \\ \vspace{0.1cm}

In order to use the WebRTC API for peer to peer connections we
will have to set up a signalling server as explained in 
section \ref{sec:research}. Signalling servers aren't
available free of charge, for example Google Firebase charges
nothing for the 
first 360MB of data transfer per day and after this they charge
\$0.15 per GB. From my interview with the client I know that 
Axel would like the system to be \textit{"completely free if
at all possible."} Whilst the prices from Firebase aren't 
extortionate by any means, the reality that my client would
prefer the application to be free means that the scalabilty of
the system would be limited. After a certain amount of data is 
transfered via the signalling server the system would no longer
work meaning the number of users we could potentially have is 
capped. To justify this being a limitation we can notice 
the fact that we require a signalling server in order to
establish a network connection means that one of the client's
requests could perhaps, not be reasonably achieved. \\
\vspace{0.2cm}

\textbf{Limitation 4: } \\ \vspace{0.1cm}

If this system is to be an actual web app then I would have to 
host it on a dedicated server, then purchase a domain name for
my web app. The dedicated server would host the files needed 
for the web app to run, and the domain name would have to be 
purchased from a domain registrar so that whenever people type
this domain name they are directed to the IP address of your 
server. Unfortunately both of these things require money to
be spent whilst my client would prefer to have spent no money 
on this system. If I really want to fulfill the client's 
requests then I would have to use localhost in order to host
the website, and this may cause complications in the future, 
like where should the database be hosted? These concerns fully 
justify this limitation because it could cause great 
inconveniences in the development of the system.\\

\section{Client requirements}
% specify
%justify why they are important

\subsection{Data capture}

A microphone and video camera will be used in order to get 
video and audio footage from each user. This will enable the 
users to communicate with one another and will allow my client
to be able to host video conferences on the system. 
Justification for audio and video were provided in 
\ref{sec:computational}, so here we will justify the use of 
cameras and microphones. The approach of using microphones and
webcams to capture video and audio is fully justified by the
fact that there exists no suitable alternatives to these 
technologies. For video the only other known alternative to a
camera is to use a photogram. A photogram is a black and white
image \textit{"made by placing objects between a light 
sensitive paper or film and light source."} \cite{photo}. This
is unsuitable for video as if we want to achieve a standard
frame rate of 30 FPS the users would have to buy a large
quantity of photographic paper, costing the user a lot of
money. Furthermore photograms take roughly 1 minute to
develop, this means that the user would have to properly setup,
develop and share photograms with others at a rate of 30 times
per second, whilst waiting 1 minute for each photogram to
develop. These reasons provide sufficient justification as for
why cameras are the only suitable option. As for audio my 
independent research on this topic indicated that we have not
yet found alternatives to microphones for capturing sound. 

\subsection{Data verification and validation}

In this system data will be verified upon the creation of a
new account. Users will prompted to enter their desired
password twice in order to ensure that the user would really 
like this to be their password and that they have spelt it 
correctly. Moreover these passwords will be checked to 
ensure that they are of suitable strength. Justification for 
this feature was provided in \ref{sec:features} under 
\textit{Usernames and passwords to join a call}.

\subsection{Outputs}

\subsection{User Interface}

\subsection{Security Issues}

\subsection{Backing up data}

\subsection{Software requirements}

\subsection{Hardware requirements}

\section{Success criteria}
